---
title: "Package metrics!"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(pkgstats)
library(purrr)
library(DT)
library(pkgsearch)

df3 <- readRDS("df3.rds")
```

## Explore package metrics data

Here are some possible questions we could build our trivia questions around:

* [x] Which package in the tidyverse has the most lines of R code? [q1](#q1)
* [x] Which package has the most data files included? [q2](#q2)
* [x] Which package in the core of tidymodels has the most lines of test code? (#tidymodelsimport) [q3](#q3)
* [x] How many vignettes are available across CRAN? [q4](#q4)
* [x] Which package has the most Rs in its name? [q5](#q5)
* [x] What package has the most contributors? [q6](#q6)
* [x] Which package has the highest median number of parameters per exported function? [q7](#q7)
* [x] Which package has the most median number of documentation lines per function? [q8](#q8)
* [x] Which of the following packages that imports htmlwidgets has the most lines of comments? [q9](#q9)
* [x] Which package has the longest name, excluding special characters or punctuation characters? [q10](#q10)


* [ ] Which of the following packages in the shiny ecosystem have the most functions?
* [ ] How many R packages on CRAN serve data sets?
* [ ] Which of the following packages has the most if statements?
* [ ] What package other than `{tidyverse}` has the most recursive dependencies?

* [ ] How many deprecated color packages?

* [ ] How many packages still remain from R 1.4?
* [ ] What package has the most versions published on CRAN?
* [ ] Other than R and C/C++, what is the most compiled language that R wraps around?
* [ ] Which author has published the most packages?
* [ ] Which package has the longest/shortest name?
* [ ] What proportion of packages use `.` instead of camel case?
* [ ] How many packages use a capital R other than as the first letter?

* [ ] Which packages have the longest and shortest names?
* [ ] How many packages have function names that namespace themselves (i.e. stringr has `str_` functions to namespace)

* [ ] Which package has the least number of lines?
* [ ] Which package has the most amount of documentation (or documentation to code ratio)
* [ ] (TO DO: See if packages are written in different languages)
* [ ] Which function has the most amount of lines and what package is it from?
* [ ] Out of all of the package maintainers, what are the top 10 email domains?
* [ ] clyclomatic complexity
* [ ] How many packages import Shiny?
* [ ] How many packages import `%>%` (magrittr)?

* [ ] Which package has the lowest median number of parameters per exported function?

### Exploring for answers

```{r}
df3 <- df3 %>%
  mutate(n_depends = ifelse(depends == "NA", 0, stringr::str_count(depends, ",") + 1)) %>%
  mutate(n_imports = ifelse(imports == "NA", 0, stringr::str_count(imports, ",") + 1)) %>%
  mutate(dependency_total = n_depends + n_imports)
```

#### Which package in the tidyverse has the most lines of R code? {#q1}

```{r}
# step one: grab all tidyverse packages
q1_imports <- df3 %>%
  filter(package == "tidyverse") %>%
  select(package, imports, depends, suggests) %>%
  pull(imports) %>%
  stringr::str_split(., ",") %>%
  .[[1]] %>%
  stringr::str_trim(.)

# which tidyverse package has the most lines of R code
q1_db <- df3 %>%
  filter(package %in% q1_imports) %>%
  select(package, loc_R, loc_src, blank_lines_R, comment_lines_R) %>%
  arrange(desc(loc_R))

most_meta <- cran_packages(pull(q1_db, package))

q1_db <- left_join(q1_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q1_answer <- "ggplot2"
q1_incorrect <- c("rlang", "dplyr", "lubridate")

q1_final_db <- q1_db %>%
  filter(package %in% c(q1_answer, q1_incorrect))

q1_total_code <- q1_final_db %>%
  slice(1) %>%
  pull(loc_R)

q1_entry <- list(
  quiz = 1,
  qid = 1,
  question_text = "Which package in the tidyverse (within the core or specialized packages) has the most lines of R code?",
  answer_text = glue::glue("Within the tidyverse, {q1_answer} has {q1_total_code} lines of R code!"),
  type = "choice",
  choices_value = q1_final_db$package,
  choices_text = q1_final_db$choice_string,
  answer = q1_answer
)

```


#### Which package has the most data files included? {#q2}

```{r}
q2_db <- df3 %>%
  arrange(desc(num_data_files)) %>%
  select(package, data_size_median, num_data_files, data_size_total) %>%
  slice(1:50)

most_meta <- cran_packages(pull(q2_db, package))

q2_db <- left_join(q2_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q2_answer <- "Devore7"
q2_incorrect <- c("openintro", "fivethirtyeight", "Lock5Data")

q2_final_db <- q2_db %>%
  filter(package %in% c(q2_answer, q2_incorrect))
  
q2_datafiles <- q2_final_db %>%
  slice(1) %>%
  pull(num_data_files)


q2_entry <- list(
  quiz = 1,
  qid = 2,
  question_text = "Which package on CRAN has the most data files?",
  answer_text = glue::glue("The {q2_answer} package that accompanies the classic Probability and Statistics for Engineering and the Sciences (authored by Jay Devore) contains {q2_datafiles}! Who knows, maybe one of these sets will be featured on a future Tidy Tuesday?"),
  type = "choice",
  choices_value = q2_final_db$package,
  choices_text = q2_final_db$choice_string,
  answer = q2_answer
)
```

#### Which package in the core of `tidymodels` has the most lines of test code? {#q3}

```{r tidymodels}
q3_core <- c("rsample", "parsnip", "recipes", "workflows", "tune", "yardstick", "broom", "dials")

q3_imports <- df3 %>%
  filter(package == "tidymodels") %>%
  select(package, imports, depends, suggests) %>%
  pull(imports) %>%
  stringr::str_split(., ",") %>%
  .[[1]] %>%
  stringr::str_trim(.)

q3_db <- df3 %>%
  filter(package %in% q3_core) %>%
  select(package, loc_tests) %>%
  arrange(desc(loc_tests))

most_meta <- cran_packages(pull(q3_db, package))

q3_db <- left_join(q3_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q3_answer <- "recipes"
q3_incorrect <- c("broom", "tune", "yardstick")

q3_final_db <- q3_db %>%
  filter(package %in% c(q3_answer, q3_incorrect))

q3_loc_tests <- q3_final_db %>%
  filter(package == q3_answer) %>%
  pull(loc_tests)
q3_entry <- list(
  quiz = 1,
  qid = 3,
  question_text = "Which package in the core of tidymodels has the most lines of test code?",
  answer_text = glue::glue("The leader of the testing pack in the tidymodels core is {q3_answer} with {q3_loc_tests} lines of testing code! Sign me up for testing if you see any pizza recipes that need a little attention ..."),
  type = "choice",
  choices_value = q3_final_db$package,
  choices_text = q3_final_db$choice_string,
  answer = q3_answer
)
```

#### Total vignettes on CRAN? {#q4}

```{r}
q4_answer <- df3 %>% 
  summarize(n_vignettes_total = sum(num_vignettes, na.rm = TRUE)) %>%
  pull(n_vignettes_total)

q4_entry <- list(
  quiz = 1,
  qid = 4,
  question_text = "How many package vignettes are available across the entire CRAN package library? Values that are within 250 of the correct total (either under or over) will count!",
  answer_text = glue::glue("Can you believe their are {q4_answer} vignettes across the entire CRAN package library? That is a lot of reading material!"),
  type = "number",
  answer = q4_answer
)
```

#### Which package has the most R's in the name? {#q5}

```{r}
# how many R's in the package name
q5_db <- df3 %>%
  mutate(n_letters_R = stringr::str_count(package, "r|R")) %>%
  select(package, n_letters_R) %>%
  arrange(desc(n_letters_R)) %>%
  slice(1:50)

most_meta <- cran_packages(pull(q5_db, package))

q5_db <- left_join(q5_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q5_answer <- q5_db %>%
  slice(1) %>%
  pull(package)

q5_entry <- list(
  quiz = 1,
  qid = 5,
  question_text = "Which package has the most R's in its name? Both upper and lower-case versions count. The correct spelling of the package (irrespective of case) will be accepted. Hint: If the package had a favorite type of clothing, it would likely have a closet full of jeans!",
  answer_text = "The honor goes to tigreBrowserWriter, the package that empowers you to write gene expression model results into the database format used by the tigreBrowser, part of the innovative Bioconductor suite of packages for powerful bioinformatics and genetic analyses with R.",
  type = "text",
  answer = q5_answer
)
```

#### Which package has the most contributors? {#q6}

```{r}
q6_db <- df3 %>%
  mutate(n_total_contrib = desc_n_aut + desc_n_ctb) %>%
  select(package, n_total_contrib) %>%
  arrange(desc(n_total_contrib)) %>%
  slice(1:50)

most_meta <- cran_packages(pull(q6_db, package))

q6_db <- left_join(q6_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q6_answer <- "mlpack"
q6_incorrect <- c("broom", "rcorpora", "data.table")

q6_final_db <- q6_db %>%
  filter(package %in% c(q6_answer, q6_incorrect))

# todo create ggplot
q6_entry <- list(
  quiz = 1,
  qid = 6,
  question_text = "Which package has the most contributors? This includes both the author (aut) and contributor (ctb) roles for a package.",
  answer_text = "The mlpack package leads the way with 137 authors and contributors! I can't say I am too surprised as writing a machine learning library in only C++ code alongside bindings to other languages is no small task.",
  type = "choice",
  choices_value = q6_final_db$package,
  choices_text = q6_final_db$choice_string,
  answer = q6_answer
)
```



#### Which package has the highest median parameters per exported function? {#q7}

```{r}
most_exp <- arrange(df3, desc(npars_exported_md)) %>% 
  slice(1:50) %>%
  select(package, npars_exported_md)

#most_exp

# grab metadata of the top 50
pkg_most_names <- most_exp %>%
  pull(package)

most_meta <- cran_packages(pkg_most_names)

most_exp <- left_join(most_exp, most_meta, by = c("package" = "Package"))

q7_answer <- "lchemix"
q7_incorrect <- c("stargazer", "BioVenn", "ggrisk")

q7_final_db <- most_exp %>%
  filter(package %in% c(q7_answer, q7_incorrect)) %>%
  mutate(choice_string = glue::glue("{package}: {Title}")) %>%

  select(package, choice_string, npars_exported_md)

q7_entry <- list(
  quiz = 1,
  qid = 7,
  question_text = "Which package has the highest median parameters per exported function?",
  answer_text = "The lchemix package has a median of 91 parameters per exported function. That is a lot of parameters!",
  type = "choice",
  choices_value = q7_final_db$package,
  choices_text = q7_final_db$choice_string,
  answer = q7_answer
)
```

#### Which package has the most median number of documentation lines per function? {#q8}

```{r}
q8_db <- arrange(df3, desc(doclines_per_fn_exp_md)) %>% 
  slice(1:50) %>%
  select(package, doclines_per_fn_exp_md, doclines_per_fn_exp_mn, docchars_per_par_exp_mn, docchars_per_par_exp_md)

most_meta <- cran_packages(pull(q8_db, package))

q8_db <- left_join(q8_db, most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q8_answer <- "tidySEM"
q8_incorrect <- c("rtables", "mapview", "dreamer")

q8_final_db <- q8_db %>%
  filter(package %in% c(q8_answer, q8_incorrect))

q8_doc_lines <- q8_final_db %>%
  filter(package == q8_answer) %>%
  pull(doclines_per_fn_exp_md)

q8_entry <- list(
  quiz = 1,
  qid = 8,
  question_text = "Which package has the highest median number of documentation lines per function?",
  answer_text = glue::glue("Nothing beats excellent documentation, and the {q8_answer} package is chock full of documentation with approximately {q8_doc_lines} median documentation lines per function!"),
  type = "choice",
  choices_value = q8_final_db$package,
  choices_text = q8_final_db$choice_string,
  answer = q8_answer
)

```

#### Which of the following packages that imports htmlwidgets has the most comments in R files? {#q9}
```{r}
# rinterface_packages <- c("bs4Dash", "shinydashboardPlus", "argonDash", "tablerDash", "argonR", "shinybulma", "shinyMobile",  "shinyEffects", "fullPage", "mobileCharts")

# q9_db <- df3 %>%
#   filter(package %in% rinterface_packages) %>%
#   arrange(desc(n_fns_r)) 


q9_htmlwidgets_imports <- df3 %>%
  mutate(imports_split = purrr::map(imports, ~stringr::str_split(.x, ",")[[1]])) %>%
  mutate(imports_htmlwidgets = purrr::map_lgl(imports_split, function(x) {
    x <- stringr::str_trim(x)
    res <- "htmlwidgets" %in% x
    return(res)
  })) %>%
  #select(package, imports, imports_split, imports_shiny, n_fns_r) %>%
  arrange(desc(comment_lines_R)) %>%
  #filter(package == "shinydashboard")
  filter(imports_htmlwidgets) %>%
  select(package, n_fns_r, n_fns_per_file_r, comment_lines_R)

most_meta <- cran_packages(pull(q9_htmlwidgets_imports, package))

q9_db <- q9_htmlwidgets_imports %>%
  left_join(most_meta, by = c("package" = "Package")) %>%
  mutate(choice_string = glue::glue("{package}: {Title}"))

q9_answer <- "DiagrammeR"
q9_incorrect <- c("echarts4r", "plotly", "visNetwork")

q9_final_db <- q9_db %>%
  filter(package %in% c(q9_answer, q9_incorrect))

q9_loc_comments <- q9_final_db %>%
  filter(package == q9_answer) %>%
  pull(comment_lines_R)
q9_entry <- list(
  quiz = 1,
  qid = 9,
  question_text = "Which of the following packages that imports htmlwidgets has the most comment lines in R files?",
  answer_text = glue::glue("Low and behold, the {q9_answer} package authored by the first keynote speaker of R/Pharma 2021 Richard Iannone takes the crown with {q9_loc_comments} comment lines! Fun fact: Richard discussed the early developments and origin story of gt with Eric Nantz in episode 27 of the R-Podcast."),
  type = "choice",
  choices_value = q9_final_db$package,
  choices_text = q9_final_db$choice_string,
  answer = q9_answer
)
```



#### Which package has the longest name, excluding special characters or punctuation characters? {#q10}

```{r}
q10_db <- df3 %>%
  mutate(package_clean = stringr::str_replace_all(package, "[[:punct:]]", "")) %>%
  mutate(pkg_n_letters = stringr::str_length(package_clean)) %>%
  select(package, package_clean, pkg_n_letters) %>%
  arrange(desc(pkg_n_letters)) %>%
  slice(1:50)

q10_answer <- q10_db %>%
  slice(1) %>%
  pull(package)


q10_entry <- list(
  quiz = 1,
  qid = 10,
  question_text = "Which package has the longest name, excluding special characters or punctuation characters? The correct spelling of the package (irrespective of case) will be accepted. Hint: The statistical methods in this package would be a great fit to predicting whether the conference attendees like taking this quiz (or not)!",
  answer_text = glue::glue("The longest name trophy (virtual of course) goes to the {q10_answer} package!"),
  type = "text",
  answer = q10_answer
)
  
```

## Assembline quiz questions

```{r}
quiz1_items <- list(
  q1_entry, q2_entry, q3_entry, q4_entry, q5_entry, q6_entry, q7_entry, q8_entry, q9_entry, q10_entry
)

saveRDS(quiz1_items, "prototyping/quiz1_items.rds")
```